### 2018-01-06 icde/revision/sec-app.tex

\begin{example} \label{eg-model-citation}
\markedb{Figure~\ref{fig-example-graph} shows a real-life example of the heterogeneous academic graph, which is drawn based on the following four articles as well as their citation relationships:}

@@

\markedb{The corresponding citation graph is also presented in Fig.~\ref{fig-example-graph} where the four nodes represent articles A, B, C and D, and edges represent the citations between them. Note that each node is also associated with time information (we omit the peak time on each node since it can only be computed when all the citations are given).}
\end{example}

\markedb{The importance of articles is then computed as follows.}

@@

\begin{example} \label{eg-model-venue}
\markedb{Recall the heterogeneous academic graph in Fig.~\ref{fig-example-graph}. Its corresponding venue graph is also presented. Note that two nodes in the venue graph are related to venue {\em TKDE} since each node denotes a venue in a specific year. There is an edge from nodes {\em TKDE-15} to {\em TKDE-14} since article A published in {\em TKDE-15} cites article B published in {\em TKDE-14}. And it is similar to derive other edges in the venue graph.}
\end{example}

@@

\begin{example} \label{eg-model-author}
\markedb{We also include the corresponding author citation graph in Fig.~\ref{fig-example-graph}. Observe that six links in the author citation graph are generated between authors \{{\em Ryan}, {\em Nesreen}\} to \{{\em Charu}, {\em Yuchen}, {\em Philip}\} given a single citation from articles A to B. And it is quite obvious that the number of edges in the author citation graph is much larger than the one in the citation graph, which verifies our claim above.}
\end{example}

@@

\begin{example} \label{eg-ranking}
\markedb{Figure~\ref{fig-example-ranking} illustrates an example of the importance assembling procedure. 
Consider an article $v$ published by authors $t$ and $u$ in venue $k$. 
(a) It first extracts the importance $c_v$ of article $v$ computed by the  citation component and properly scales $c_v$ to citation importance score $R_c(v)$.
Similarly, (b) it derives the venue importance score $R_v(v)$ based on the venue importance $v_k$ of venue $k$ computed  by the venue component.
(c) The author importance score $R_a(v)$ averages and scales the author importance $a_t$ and $a_u$ of authors $t$ and $u$ computed  by the author component.
Finally, (d) the three importance scores are aggregated to the final ranking score $R(v)$. }
\end{example}

>>>>

\begin{example} \label{eg-model-citation}
Figure~\ref{fig-example-graph} shows a real-life example of the heterogeneous academic graph, which is drawn based on the following four articles as well as their citation relationships:

@@

The corresponding citation graph is also presented in Fig.~\ref{fig-example-graph} where the four nodes represent articles A, B, C and D, and edges represent the citations between them. Note that each node is also associated with time information (we omit the peak time on each node since it can only be computed when all the citations are given).
\end{example}

The importance of articles is then computed as follows.

@@

\begin{example} \label{eg-model-venue}
Recall the heterogeneous academic graph in Fig.~\ref{fig-example-graph}. Its corresponding venue graph is also presented. Note that two nodes in the venue graph are related to venue {\em TKDE} since each node denotes a venue in a specific year. There is an edge from nodes {\em TKDE-15} to {\em TKDE-14} since article A published in {\em TKDE-15} cites article B published in {\em TKDE-14}. And it is similar to derive other edges in the venue graph.
\end{example}

@@

\begin{example} \label{eg-model-author}
We also include the corresponding author citation graph in Fig.~\ref{fig-example-graph}. Observe that six links in the author citation graph are generated between authors \{{\em Ryan}, {\em Nesreen}\} to \{{\em Charu}, {\em Yuchen}, {\em Philip}\} given a single citation from articles A to B. And it is quite obvious that the number of edges in the author citation graph is much larger than the one in the citation graph, which verifies our claim above.
\end{example}

@@

\begin{example} \label{eg-ranking}
Figure~\ref{fig-example-ranking} illustrates an example of the importance assembling procedure.
Consider an article $v$ published by authors $t$ and $u$ in venue $k$.
(a) It first extracts the importance $c_v$ of article $v$ computed by the  citation component and properly scales $c_v$ to citation importance score $R_c(v)$.
Similarly, (b) it derives the venue importance score $R_v(v)$ based on the venue importance $v_k$ of venue $k$ computed  by the venue component.
(c) The author importance score $R_a(v)$ averages and scales the author importance $a_t$ and $a_u$ of authors $t$ and $u$ computed  by the author component.
Finally, (d) the three importance scores are aggregated to the final ranking score $R(v)$. 
\end{example}
